Data- and Systems Paper: Identifying Handicap Parking Spots for Event's Venues

### 2016-04-07 milestone1/paper/paper.tex
report update
smth

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{first@vu.nl} \and \url{second@vu.nl}}

@@

Hereby we provide three concrete use-cases where our application's benefits are to be maximized.

@@

>>>>

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{\url{d.alivanistos@student.vu.nl} \and \url{s.baezsantamaria@student.vu.nl} \and \url{a.jemmett@student.vu.nl}}

@@

Hereby we provide three concrete use-cases where our application's benefits are to be maximized. A general use-case diagram is provided in Figure \ref{fig:use-case}.

@@

\begin{figure}[h]
	\centering
	\includegraphics[width=1\textwidth]{img/use-case-diagram.png}
	\caption{Use case diagram for our web application}
	\label{fig:use-case}
\end{figure}
